---
title: "Anna Ehrhorn Assignment #7"
output: html_notebook
---


***
Question 1
A function that runs a linear regression and return a logical
of the residuals that are the largest number with the following factors:
x = explantory variable
y = response variable
p = a number

```{r}
lm.regress.resids <- function(x, y, p) {
  regression.model <- lm(y ~ x)
  absolute.resids <- abs(regression.model$residuals)
  sort.resids <- sort(absolute.resids, decreasing = TRUE)
  cutoff <- sort.resids[p]
  logical.resids <- (absolute.resids >= cutoff)
  return(logical.resids)
}
```


Testing the developed function
```{r}
x <- c(4, 5, 2, 8, 5, 9, 10, 1)
y <- c(2, 6, 8, 1, 9, 2, 10, 3)

testlm <- lm(y~x)
attributes(testlm)
testlm$residuals
lm.regress.resids(x, y, 3)
```
***


***
Question 2
Plot a scatterploy with a regression line of a quantitative response and 
explanatory variable, and highlight the 10% largest residuals on the 
scatterplot.
(n >= 50).

```{r include=FALSE}
library(here)

hsb2 <- read.csv(here("Data", "hsb2.csv"))
```

```{r}
p <- round(0.1*(nrow(hsb2)))

regress.resids <- lm.regress.resids(hsb2$read, hsb2$write, 20)

cor.write.read <- cor(hsb2$read, hsb2$write)

regress.lm.model <- lm(hsb2$write ~ hsb2$read)

plot(hsb2$read, hsb2$write,
     main = "Relationship between High School Reading and Writing Achievement",
     xlab = "Standardized Reading Achievement Score",
     ylab = "Standardized Writing Achievement Score",
     col = ifelse(regress.resids == TRUE, "blue", "black"),
     pch = ifelse(regress.resids == TRUE, 15, 0))
abline(regress.lm.model)
```
***
