---
title: "Anna Ehrhorn Assignment #7"
output: html_notebook
---

Question 1
A function that runs a linear regression and return a logical
of the residuals that are the largest number with the following factors:
x = explantory variable
y = response variable
p = a number

```{r}
lm.regress.resids <- function(x, y, p) {
  regression.model <- lm(y ~ x)
  resids <- regression.model$residuals
  absolute.resids <- abs(resids)
  sort.resids <- sort(absolute.resids, decreasing = TRUE)
  cutoff <- sort.resids[p]
  logical.resids <- (absolute.resids >= cutoff)
  return(logical.resids)
}
```

Testing function
```{r}
x <- c(4, 5, 2, 8, 5, 9, 10, 1)
y <- c(2, 6, 8, 1, 9, 2, 10, 3)

testlm <- lm(y~x)
attributes(testlm)
testlm$residuals
lm.regress.resids(x, y, 3)
```

Question 2
Plot a scatterploy with a regression line of a quantitative response and 
explanatory variable, and highlight the 10% largest residuals on the 
scatterplot.
(n >= 50).

```{r include=FALSE}
library(here)

my.data <- read.csv(here("XX.csv"))  #decide on dataset
```

```{r}
lm.regress.resids(x, y, 10) #enter in variables

plot(correlation, col = "blue")
              abline(regression.model)
              


```

