---
title: "Anna Ehrhorn Assignment #7"
output: html_notebook
---

Question 1
A function that runs a linear regression and prints a logical
of the residuals that are the largest certain % with the following factors:
x = explantory variable
y = response variable
p = a number

```{r}
lm.regress.resids <- function(x, y, p) {
  descriptives <- summary(my.data)
  correlation <- cor(x, y)
  regression.model <- lm(y ~ x,
            data = my.data)
  regress.model.sum <- summary(regression.model)
  resids <- regression.model$residuals
  absolute.resids <- abs(resids)
  logical.resids <- as.logical(sort(absolute.resids) #how to select 10%
  return(logical.resids)
  print(plot(correlation, col = "blue")
              abline(regression.model))
}
```


Question 2
Plot a scatterploy with a regression line of a quantitative response and 
explanatory variable, and highlight the 10% largest residuals on the 
scatterplot.
(n >= 50).

```{r include=FALSE}
library(here)

my.data <- read.csv(here("XX.csv"))  #decide on dataset
```

```{r}
lm.regress.resids(x, y, 10) #enter in variables
```

